Forecasting biodiversity in breeding birds using best practices

### 2017-12-09 manuscript/draft.Rmd
update details of environmental methods
Saying we did not use the calendar year is an important detail.
Updated months used in the NDVI calcs as per the current code.

**Past environmental data.** Environmental data included a combination of
elevation, bioclimatic variables and a remotely sensed vegetation index (the
normalized difference vegetation index; NDVI), all of which are known to
influence richness and distribution in the BBS data [@kent2014]. For each year
in the dataset, we used the 4 km resolution PRISM data [@prism] to calculate
eight bioclimatic variables identified as relevant to bird distributions
[@harris2015]: mean diurnal range, isothermality, max temperature of the warmest
month, mean temperature of the wettest quarter, mean temperature of the driest
quarter, precipitation seasonality, precipitation of the wettest quarter, and
precipitation of the warmest quarter. Satellite-derived NDVI, a primary
correlate of richness in BBS data [@hurlbert2002], was obtained from the NDIV3g
dataset with an 8 km resolution [@pinzon2014] and was available from 1981-2013.
Average summer (May, June, July) and winter (December, January, Feburary) NDVI
values were used as predictors. Elevation was from the SRTM 90m elevation
dataset [@jarvis2008] obtained using the R package raster [@raster].
Because BBS routes are 40-km transects rather than point counts, we used the
average value of each environmental variable within a 40 km radius of each BBS
route's starting point.

>>>>

**Past environmental data.** Environmental data included a combination of
elevation, bioclimatic variables and a remotely sensed vegetation index (the
normalized difference vegetation index; NDVI), all of which are known to
influence richness and distribution in the BBS data [@kent2014]. For each year
in the dataset, we used the 4 km resolution PRISM data [@prism] to calculate
eight bioclimatic variables identified as relevant to bird distributions
[@harris2015]: mean diurnal range, isothermality, max temperature of the warmest
month, mean temperature of the wettest quarter, mean temperature of the driest
quarter, precipitation seasonality, precipitation of the wettest quarter, and
precipitation of the warmest quarter. These variables were calculated for the 12
months leading up to the annual survey (July-June) as opposed to the calendar
year. Satellite-derived NDVI, a primary correlate of richness in BBS data
[@hurlbert2002], was obtained from the NDIV3g dataset with an 8 km resolution
[@pinzon2014] and was available from 1981-2013. Average summer (April, May, June)
and winter (December, January, Feburary) NDVI values were used as predictors.
Elevation was from the SRTM 90m elevation dataset [@jarvis2008] obtained using
the R package raster [@raster]. Because BBS routes are 40-km transects rather
than point counts, we used the average value of each environmental variable
within a 40 km radius of each BBS route's starting point.
